UGAN: Underwater Image Restoration using Generative Adversarial Networks

### 2017-09-11 files/paper/paper.tex
update

\usepackage{graphicx}
\graphicspath{{images/}}

@@

\begin{figure}[!htb]
   \begin{center}$
      \begin{array}{cccc}
         \includegraphics[width=3in]{figure1}
      \end{array}$
   \end{center}
   \caption{Underwater images showing the vast divesity of noise that can occur, including
   different hues of green and blue, as well as particles in the water.}
\end{figure}

>>>>

\usepackage{graphicx}
\graphicspath{ {images/}{images/figure1/} }
%\graphicspath{{images/failures/}}
%\graphicspath{{images/figure1/}}

@@

   \includegraphics[width=0.8in]{n01496331_7428_f1} &
   \includegraphics[width=0.8in]{n01496331_16340_f1} &
   \includegraphics[width=0.8in]{n01914609_5148_f1} &
   \includegraphics[width=0.8in]{robot_f1} \\
   \includegraphics[width=0.8in]{n01664065_30279_f1} &
   \includegraphics[width=0.8in]{n01917289_5711_f1} &
   \includegraphics[width=0.8in]{n01917289_4087_f1} &
   \includegraphics[width=0.8in]{n02607072_10395_f1} \\

\end{tabular}
\caption{Sample underwater images displaying the diversity of distortion that can occur. \textbf{Maybe say something about how
some images lost all color, but some kept some color for close objects.}}
\end{figure}
